---
title: "Hello, Penguins!"
format: 
  revealjs:
    logo: images/quarto-logo.png
    footer: "🔗 [quarto.org](https://quarto.org)"
    chalkboard: true
editor: visual
execute: 
  echo: true
---

# Introduction

## Data

For this analysis we'll use the penguins dataset from the palmerpenguins package.

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(ggthemes)
library(palmerpenguins)
library(gt)
```

## Species

The figure below is a bar plot of species of penguins.

```{r}
#| label: bill-dims-species
#| warning: false
#| fig-width: 5
#| fig-asp: 0.618
#| output-location: column-fragment
#| code-line-numbers: "|3-8|11|16"

ggplot(
  penguins,
  aes(
    x = bill_length_mm, 
    y = bill_depth_mm,
    color = species, 
    shape = species
  )
) +
  geom_point() +
  scale_color_colorblind() +
  labs(
    x = "Bill length (mm)", 
    y = "Bill depth (mm)"
  ) +
  theme_minimal()
```

## Penguins

The table below shows the first 10 penguins from the dataset.

```{r}
#| label: penguins-top10

penguins |>
  slice_head(n = 10) |>
  select(species, island, bill_length_mm, bill_depth_mm) |>
  gt()
```

# Analysis

## Model 1 results {.smaller}

-   This model is awesome

-   But has some drawbacks...

-   And here is one drawback...

-   This model is awesome

-   But has some drawbacks...

-   And here is one drawback...

-   This model is awesome

-   But has some drawbacks...

-   And here is one drawback...

## Model 2 results

::: columns
::: {.column width="20%"}
Column 1 content

blah

blah

-   item 1

-   item 2
:::

::: {.column width="20%"}
Column 2 content

blah

blah
:::

::: {.column width="60%"}
Column 3 content

hello

mello

```{r}
plot(cars)
```
:::
:::

## Model 3

::: panel-tabset
## definition

I define model here

## output

show the output here
:::
